\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\color{BrickRed}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{BrickRed}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
  {\LARGE \scshape Maria Shurui Ma} \\ \vspace{5pt}
  \small \raisebox{-0.1\height}\faPhone\ (819) 329-8678~ \href{mailto:maria.shurui.ma@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{maria.shurui.ma@gmail.com}} ~
  \href{https://www.linkedin.com/in/maria-shurui-ma}{\raisebox{-0.2\height}\faLinkedin\ \underline{maria-shurui-ma}}  ~
  \href{https://github.com/MariaMa-GitHub}{\raisebox{-0.2\height}\faGithub\ \underline{MariaMa-GitHub}} ~
  \href{https://mariama-github.github.io/developer-portfolio/}{\raisebox{-0.2\height}\faGlobe\ \underline{Portfolio}}
  \vspace{-8pt}
\end{center}

\vspace{-10pt}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Toronto}{Sep 2022 -- Jun 2026}{Honours Bachelor of Science --- Computer Science Specialist}{GPA: 3.80/4.00}
\resumeItemListStart
\resumeItem{Relevant Coursework: Software Engineering, Web Development, Algorithm Design \& Analysis, Operating Systems, Databases, Machine Learning, Neural Networks and Deep Learning}
\resumeItem{Academic Achievements: Dean's List Scholar}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-15pt}



% -----------EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{University of Toronto, Department of Computer Science}{Sep 2025 -- Dec 2025}
{Teaching Assistant --- CSC207 Software Design}{Toronto, Canada}
\resumeItemListStart
\resumeItem{Facilitated weekly 2-hour tutorial sessions for 30 students in an 870-student course, leading hands-on labs on object-oriented design, design patterns, and software development practices in Java.}
\resumeItem{Graded midterm and final exams; mentored student teams on group software projects, guiding them through clean architecture, version control with Git, and agile workflows.}
\resumeItemListEnd

\resumeSubheading
{Runwei™ $\vert$ AI \& ML for Financial Inclusion and Economic Mobility}{Jan 2025 -- Apr 2025}
{Full-Stack Developer}{Toronto, Canada}
\resumeItemListStart
\resumeItem{Built and launched a browser extension and mobile app to automate scraping, processing, and publishing of business opportunity data from diverse sources.}
\resumeItem{Leveraged OpenAI API for intelligent extraction and classification of unstructured business data from 5+ source formats, reducing manual processing time.}
\resumeItem{Implemented automated testing with unit, integration, and end-to-end tests using Jest, Cypress, and Maestro, achieving 95\%+ coverage and building a CI/CD pipeline with GitHub Actions.}
\resumeItemListEnd

\resumeSubheading
{Students Developing Software (SDS) Team}{Jan 2024 -- Apr 2024}
{Software Developer}{Toronto, Canada}
\resumeItemListStart
\resumeItem{Implemented a custom PEP8 code style renderer and developed new static analysis checks for PyTA, a Python linting tool used by 1,500+ students per semester at UofT.}
\resumeItem{Contributed to the full software development lifecycle through documentation, unit testing, debugging, and code review across 10+ pull requests.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}



%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart
\resumeProjectHeading{\href{https://github.com/MariaMa-GitHub/EyeHearU}{\textbf{Eye Hear U}}}{Jan 2026 -- Present}
\resumeItemListStart
\resumeItem{Building an iOS app that translates American Sign Language (ASL) into English text and speech in real time, using a \textbf{PyTorch} 3D CNN video classifier (R3D-18) trained on 129K+ videos across 2,000+ sign classes.}
\resumeItem{Engineered a data pipeline to ingest and unify three public ASL datasets, and deployed a \textbf{FastAPI} inference backend on \textbf{AWS ECS Fargate} with infrastructure provisioned via \textbf{Terraform}.}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading{\href{https://justcookiedough.itch.io/soothsayer}{\textbf{Soothsayer}}}{Sep 2025 -- Dec 2025}
\resumeItemListStart
\resumeItem{Programmed core game mechanics and card systems for a single-player narrative card game in \textbf{Unity} and \textbf{C\#}, featuring tarot-based card synergies that shape branching character storylines.}
\resumeItem{Collaborated in a 9-person cross-disciplinary team of programmers, artists, and sound designers, shipping final builds for Windows and macOS published on Itch.io.}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading{\href{https://github.com/MariaMa-GitHub/scriptorium}{\textbf{Scriptorium}}}{Sep 2024 -- Dec 2024}
\resumeItemListStart
\resumeItem{Developed an online platform for writing, executing, and sharing code in 10 programming languages.}
\resumeItem{Built a full-stack web application using \textbf{React} and \textbf{Tailwind CSS} on the frontend and \textbf{Next.js}, \textbf{Docker}, and \textbf{Prisma} on the backend, adhering to \textbf{RESTful API} principles.}
\resumeItemListEnd
\vspace{-13pt}

\resumeSubHeadingListEnd
\vspace{-3pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item{
        \textbf{Programming}{: Python, Java, C, C++, C\#, HTML, CSS, JavaScript, TypeScript, SQL, Haskell.} \\
        \textbf{Frameworks \& Libraries}{: React, React Native, Next.js, Node.js, Express, FastAPI, Flask, PyTorch, Unity, Tailwind CSS, Prisma, Pandas, NumPy.} \\
        \textbf{Tools \& Platforms}{: AWS (S3, ECS, Fargate), Terraform, Docker, Firebase, PostgreSQL, Git, GitHub Actions, Jest, Cypress, Linux.} \\
        \textbf{Languages}{: English, French, Mandarin, Spanish.} \\
        }
\end{itemize}
\vspace{-15pt}


\end{document}
